Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
small typos and rewrite

	In this section the current description of the C-space of synchronous
	constrained systems is reviewed, mostly through
	\cite{george2009characterization}.

@@

		We consider a discrete timeline and systems comprised of periodic concrete
		tasks with constrained deadlines on uniprocessor platforms, where each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
			\item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval during which there is always
			at least one job available and not finished in the system and maximal
			(in interval length) with this property. Any busy period starts and ends
			with an idle time.
			\item The interval between the initial time and the first
			idle time is called the \emph{first busy period}.
		\end{itemize}

@@

	\begin{definition}
		The \textbf{demand-bound function (DBF)}
		\cite{baruah1999generalized, baruah1990algorithms} defined for a task set
		$\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
		time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
	\end{definition}

>>>>

	In this section the current description of the C-space of synchronous
	constrained systems, which has been mostly covered by \cite{george2009characterization}, is reviewed.

@@

		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
			\item $H = \operatorname{lcm}(T_0, \cdots, T_{n-1})$
			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval during which there is always
			at least one unfinished job available in the system and maximal
			with this property. Any busy period starts and ends
			with an idle time.
			\item The interval between the initial time and the first
			idle time is called the \emph{first busy period}.
		\end{itemize}

@@

	\begin{definition}
		The \textbf{demand-bound function (DBF)}
		defined for a task set $\tau$ and noted $\dbf{t_1, t_2}$, is equal to
		the maximal cumulated execution time of jobs of $\tau$ contained in the
		closed interval $[t_1, t_2]$.
	\end{definition}
